---
title: "Prediction of Win Probability of FC Barcelona"
author: "kosw"
date: "2023-12-22"
output: ioslides_presentation
---

```{r, echo=FALSE}
if(system.file(package = 'png') == ""){
  install.packages('png')
}
library(png)
```


## Motivate
```{r echo=FALSE, fig.height=3, fig.width=4}
x <- "https://raw.githubusercontent.com/rejeton1/First_RMarkdown_Presentation/main/game.png"
download.file(x,'game.jpg', mode = 'wb')
pp1 <- readPNG("game.png")
plot.new() 
rasterImage(pp1,0,0,1,1)
```

With this application, you can get win probability of FC Barcelona in real time only with 3 informations following.

- The number of goals scored by FC Barcelona
- The number of goals scored by Opponent team
- Game time


## About the prediction model

For Prediction, we used 'Logistic Regression Model'

### Explanatory variables

- The number of goals scored by FC Barcelona(integer ranging from 0 to 10)

- The number of goals scored by Opponent team(also ranging from 0 to 10)

- Game time(integer ranging 0 from 90(min))

### Response variable

- Win Probability of FC Barcelona(%)
('100 - Win Probability' is Probability of draw or lose)


## Manual
```{r echo=FALSE, fig.height=3, fig.width=5}
y <- "https://raw.githubusercontent.com/rejeton1/First_RMarkdown_Presentation/main/usage.png"
download.file(y,'usage.jpg', mode = 'wb')
pp2 <- readPNG("usage.png")
plot.new() 
rasterImage(pp2,0,0,1,1)

```

The method of use of this application is following.

1. ~ 3. Select values of explanatory variables.

4. Then you can check the win probability at bottom right.


## Thank you :)






